A Simplified Plackett-Luce Likelihood Function for Rank Orders

### 2025-01-17 inst/hankin-AustrianJournalofStatistics.tex
off-by-one error fixing
typo

\begin{figure}[t]
  \begin{centering}
\includegraphics[width=4in]{ninelikes}  % ninelikes.pdf produced by very_simplified_likelihood.Rmd
\caption{Likelihood functions for $r=0(1)8$\label{ninelikes}.  Value
  of $r$ indicated in colour by its curve; vertical line shows
  $\hat{a}\simeq 0.5886$ for the case $r=4$}
\end{centering}
\end{figure}

@@

(up to an arbitrary additive constant).  Using
$\mathcal{S}^*=\log(B-1)+B\log(1-r/n)$ as an approximate support thus
incurs an error of only $\mathcal{O}(n^{-1})$.  Observing that
$\partial^2\mathcal{S}^*/\partial B^2=-(B-1)^{-2}<0$, the evaluate
would be unique; we have $\hat{B}=1-\log(1-r/n)^{-1}$, or
alternatively $\hat{a}=(1-\log(1-r/n))^{-1}$.  Compare this with the
result of asking ``what is the probability that the focal competitor
beats a randomly chosen opponent?'' to which the binomial maximum
likelihood estimate is $\frac{r-1}{n-r}$.  For repeated independent
observations $r_i,n_i$, $1\leqslant i\leqslant N$ we would have

>>>>

\begin{figure}[t]
  \begin{centering}
\includegraphics[width=4in]{ninelikes}  % ninelikes.pdf produced by very_simplified_likelihood.Rmd
\caption{Likelihood functions for $r=0(1)8$\label{ninelikes}.  Value
  of $r$ indicated in colour by its curve; vertical line shows
  $\hat{a}\simeq 0.5886$ for the case $r=5$}
\end{centering}
\end{figure}

@@

(up to an arbitrary additive constant).  Using
$\mathcal{S}^*=\log(B-1)+B\log(1-r/n)$ as an approximate support thus
incurs an error of only $\mathcal{O}(n^{-1})$.  Observing that
$\partial^2\mathcal{S}^*/\partial B^2=-(B-1)^{-2}<0$, the evaluate
would be unique; we have $\hat{B}=1-\log(1-r/n)^{-1}$, or
alternatively $\hat{a}=(1-\log(1-r/n))^{-1}$.  Compare this with the
result of asking ``what is the probability that the focal competitor
beats a randomly chosen opponent?'' to which the binomial maximum
likelihood estimate is $\frac{r-1}{n-1}$.  For repeated independent
observations $r_i,n_i$, $1\leqslant i\leqslant N$ we would have
